\documentclass{resume}

\usepackage{paralist}
\usepackage{fontawesome}

\renewcommand{\categoryfont}{\sc}
\setlength{\oddsidemargin}{1in}
\setlength{\marginparwidth}{1in}\addtolength{\marginparwidth}{-\marginparsep}
 \setlength{\evensidemargin}{\oddsidemargin}
 \setlength{\textwidth}{\paperwidth}
 \addtolength{\textwidth}{-2in}
 \addtolength{\textwidth}{-2\oddsidemargin}
 \addtolength{\textwidth}{\marginparwidth}
 \addtolength{\textwidth}{\marginparsep}
\setlength{\topmargin}{-0.5in}
\renewcommand{\labelcitem}{$\diamond$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }
\newcommand{\fourth}{$4^{\mbox{\scriptsize th}}$\ }

\author{Mark Mr\'oz}
% ---- Address --------------------------------------------------------

\address{
    \faEnvelopeSquare \quad \mbox{\small\tt markmroz95@gmail.com}\\
    \faPhoneSquare \quad (613) 983-1908\\
    \faLinkedinSquare \quad \mbox{\small\tt http://linkedin.com/in/mark-mroz}\\
    \faGithubSquare \quad \mbox{\small\tt http://github.com/mmroz}}

\begin{document}
\maketitle

% ---- Education ---------------------------------------------------

\begin{category}{Education}
\citem{University of Ottawa}, Ottawa, Canada (2015 -- 2018)
\begin{itemize}
\item Bachelor of Science in Software Engineering
\end{itemize}
\end{category}

\begin{category}{Awards \&\\ Achieved}
  \citemnotbold{ Winner of StatsCan CanDev data challenge (2018) }
  \citemnotbold{ Selected to present Roadrunner Poster at OOPSLA (2018) }
  \citemnotbold{ Selected to develop Swift WALA as part of UCOSP (2018) }
  \citemnotbold{ Second Place in the uOttawa Engineering Entrepreneurship Competition (2016) }
  \citemnotbold{ Scholarship of the Faculty of Science - Admission (2015) }
\end{category}

% ---- Skills ---------------------------------------------------

\begin{category}{Skills}
  \newcommand{\skill}[1] {\mbox{\uppercase{{#1}}\ }}
  \citemnobullet{%
    \skill{\textbf{iOS}}
    \skill{SwiftUI}
    \skill{\textbf{Swift}}
    \skill{Graphql}
    \skill{\textbf{Xcode}}
    \skill{Testflight}
    \newline
    \skill{\textbf{Ruby on Rails}}
    \skill{SPM}
    \skill{\textbf{C/C++}}
    \skill{Xcode Cloud}
	  \skill{\textbf{Java}}
    \newline
    \skill{\textbf{React}}
    \skill{Learning Rust}
    \skill{\textbf{Kotlin}}
    \skill{Android}
    \skill{\textbf{Automated Testing}}
  }
\end{category}

% ----- Employment --------------------------------------------

\begin{category}{Work \\experience}
\citem{iOS Engineer}, Block (11/2022 -- present)\\
Developed a greenfield mobile SDK supporting enterprise merchants in accepting Cash App
Pay payments responsible for over 500M per year in annualized GPV.
\citem{iOS Engineer}, Stripe (05/2021 -- 08/2022)\\
Developed the Stripe Mobile Dashboard application where merchants can visualize their business
with comprehensive charts, manage subscriptions and take payments
directly on their device.
\citem{iOS Engineer}, Shopify (05/2019 -- 05/2021)\\
Developed the Shopify Point Of Sale mobile application on iPhone and iPad in Swift that
allows merchants to manage products and inventory, customers and perform checkouts for
their brick-and-mortar stores from a single device.
\citem{Independent Software Developer}, Ottawa, Canada (03/2017 -- Present)
\begin{itemize}
  \item (2024) Designed, developed, deployed and currently provide support for an internal
    property management tool for Homestead. Employees manage building equipment and track
    service requests. The app written in using React Native in Typescript and Expo.
  \item (2022) Designed, developed, deployed and currently provide support for an internal
    timecard and project management tool for Homestead. Employees track their daily progress
    on projects and submit payroll. The back-end is written in Ruby On Rails with GraphQL and
    session management using Redis and the front-end is written in React with Typescript.
  \item (2018) Developed an iOS application in Swift for Savour Ottawa that allows
    users to make informed choices about locally sourced food. The app combines
    local storage of merchant information with dynamic content and a clean,
    simple iOS-style user experience.
  \item (2018) Designed, developed, deployed and currently provide support for an
    internal material usage tracking tool for the Homestead property management
    company. The back-end is developed in Ruby On Rails and the front-end is written
    in HTML, SCSS and Javascript and hosted on the Heroku platform. Issues are tracked
    on Github with continuous integration provided by Travis CI.
  \item (2017) Designed, developed, deployed an internal timecard tool used by the
    Homestead, Inc. property management company. Employees based in the GTA, Kingston
    and Ottawa areas use the app regularly to track their hours, get timecards approved
    and submit them to payroll. Weeks of work for their payroll staff were automated into a
    single click.
  \end{itemize}
\citem{Software Engineering Intern}, Synacor, Inc. (05/2018 -- 09/2018)\\
Full-time software engineering intern on the Synacor mobile team.
Developed iOS and Android applications for their customer, AT\&T, and ensured
their continued success by implementing Continuous Integration using Bamboo (CI).
\citem{Software Engineering Intern}, William Demant Holdings, Inc. (09/2017 -- 12/2017)\\
Full-time software engineering intern in Warsaw, Poland.
Developed iOS applications in Swift and C\# as part of the Discovery Team leveraging machine
learning to optimize patients hearing device experiences.
\citem{Software Engineering Intern}, Canada Revenue Agency (01/2017 -- 05/2017)\\
Full-time software engineering intern in Ottawa, Canada. Designed and implemented internal
and external web apps such as dashboards and data submission portals for government agencies
in collaboration with my teammates in the Finance and Benefits (FAB) Group.
\citem{Software Engineering Intern}, Mark3 Research (05/2016 -- 09/2016)\\
Full-time software engineering intern in Ottawa, Canada. Designed and implemented a suite
of automated unit and integration tests for a business solutions dashboard and configured
Jenkins to test the platform before deployment in collaboration with team members in
numerous countries.
\citem{Founder and Software Engineer}, Shortcuts (05/2015 -- 09/2015)\\
Alongside a team of two, conceptualized, defined and implemented a two-sided marketplace for
independent hair stylists to sell their services directly to the public. Developed
the pitch and presented to investors (placing second at the University of
Ottawa Engineering Entrepreneurship Competition).
Designed and implemented large portions of the iOS app.
\citem{Assistant Manager and Fish Smoker}, Whalesbone (05/2015 -- 09/2015)\\
Smoked and delivered sustainable seafood to the Ottawa, Kingston, Montreal
and Gananoque areas. Acquired new customers for the smoked seafood products within the region.
Assisted in the management of business operations at the Whalesbone including staffing,
product quality and stock.
\end{category}

% ----- Publication --------------------------------------------

% \begin{category}{Publication}
% \citemnotbold{ M. Mroz and G. Franks}: \emph{A performance experiment system supporting fast mapping of system issues.}
%     Presented at ValueTools 2009, October 20-22.
% \end{category}

% ----- Projects --------------------------------------------

\begin{category}{Projects}
\citem{WALA}, University of Ottawa (2018)\\
Worked as part of a distributed team of three \fourth year students to
design and implement a Swift to Java translator using the IBM WALA framework.
This will ultimately enable support for iOS and macOS static analysis.
The work will be presented at the OOPSLA (2018) conference in Boston, Mass.
This project was a component of my degree program.
\citem {CHIP-8 Interpreter}, Personal/Open Source (2017)\\
Designed and implemented an interpreter capable of running CHIP-8 programs in Swift.
Includes support for video, sound, keypad and timers.
\citem {DateThis}, Personal/Open Source (2016)\\
Designed and implemented a Tinder style iOS app with a Parse backend out of interest and
definitely not loneliness!
\citem {Java CookTime}, Personal/Open Source (2016)\\
Implemented a recipe viewer and editor in Java allowing individuals to store their
favorite recipes backed by a SQLite database.
This project was a component of my degree program.
\end{category}

% -------- Reference --------------------------------------------

\begin{category}{References}
\citemnobullet Available on request.
\end{category}

\end{document}
